\documentstyle[11pt,apsabinv]{article}
\nofiles
\MeetingID{SES14}
%\DateSubmitted{20141007}
\LogNumber{SES14-2014-000156}
\SubmittingMemberSurname{alonzi}
\SubmittingMemberGivenName{loreto}
%\SubmittingMemberID{61062500,USA}
\SubmittingMemberEmail{pete.alonzi@gmail.com}
\SubmittingMemberAffil{University 
of Virginia}
\PresentationType{}
\SortCategory{}{}{}{}
\received{07 Oct 
2014}
\begin{document}
\Title{The New Muon g-2 Experiment: E989 Status and 
Progress 
Update}
\AuthorSurname{alonzi}
\AuthorGivenName{loreto}
%\AuthorEmail{pete.alonzi@gmail.com}
\AuthorAffil{University 
of Virginia}
\begin{abstract}
The Higgs Boson has been discovered at the LHC. 
With the final piece of the Standard Model locked in place it is time to focus 
on the tensions around the edges. Work in the neutrino and cosmic sectors 
indicate a need for new physics at higher energy scales. A key tool in that 
search is the precision measurement of Standard Model predictions. Measurement 
of the muon anomalous magnetic moment ($a_{\mu}$) has long proven to be a 
useful guide. The measurement can be conducted with exceptional sensitivity 
using the technique first developed at CERN and most recently implemented at 
BNL where the E821 experiment measured $a_{\mu}$ to 540$\,$ppb. This 
measurement resulted in a discrepancy from the Standard Model at a level 
greater than 3$\sigma$. The New Muon g-2 experiment at Fermilab (E989) aims to 
improve this precision by a factor of 4, down to 140$\,$ppb. Coupled with 
ongoing improvements in the theoretical calculation the new result will yield 
vital clues in the search for new physics. 
The E989 collaboration is making great progress and we will discuss: the 
completion of moving the superconducting electromagnet from Brookhaven National 
Lab to Fermilab, on site construction at Fermilab, and detector development 
focusing on PbF$_{2}$ calorimetry with SiPM 
readout.
\end{abstract}
\end{document}
